On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-01 paper.tex
Added pyramid part, polished arity 1, delay 3, unary
The pyramid part still needs some work, as does the arity 1, delay 2.

I went over Reoto's arity 1, delay 3 and made some changes to make it more readable. For now I commented out the last 2 paragraphs, as they are not necessary for the proof, I think. However, here we need to add some conclusion to the arguments of the previous two subsections.
12/1
Afternoon commit
S.S. started writing an intro for TT theorem.

\usepackage{wasysym}

@@

\title{On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 granted to S.~Z.~F. and S.~S. and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~S.}
}
\author{
Szil\'{a}rd Zsolt Fazekas\inst{1} \and
Shinnosuke Seki\inst{2}\thanks{Corresponding author}}
\institute{
Akita University, 
Graduate School of Engineering Science, 
1-1 Tegate Gakuen-machi, Akita, 0108502, Japan \\
\email{szilard.fazekas@ie.akita-u.ac.jp}
\and
The University of Electro-Communications, 
Graduate School of Informatics and Engineering, 
1-5-1 Chofugaoka, Chofu, Tokyo, 1828585, Japan \\
\email{s.seki@uec.ac.jp}
}

@@

\section{Case of delay $1$}

\input{ttt}

>>>>

\usepackage{graphbox}
\usepackage{wasysym}

@@

\title{On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 granted to S.~Z.~F. and S.~S. and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~S.}
}
\author{
Szil\'{a}rd Zsolt Fazekas\inst{1} \and
Shinnosuke Seki\inst{2}\thanks{Corresponding author (\email{s.seki@uec.ac.jp})}}
\institute{
Akita University, 
Graduate School of Engineering Science, 
1-1 Tegate Gakuen-machi, Akita, 0108502, Japan \\
%\email{szilard.fazekas@ie.akita-u.ac.jp}
\and
The University of Electro-Communications, 
Graduate School of Informatics and Engineering, 
1-5-1 Chofugaoka, Chofu, Tokyo, 1828585, Japan \\
}

@@

\section{Case of delay $1$}
\input{tt_intro}
\input{tt_theorem}

### 2018-12-01 tt_intro.tex
12/1 after lunch
Afternoon commit
S.S. started writing an intro for TT theorem.

%Let $\Xi$ be a deterministic oritatami system of delay 1 and arity 2. Assume its seed $\sigma$ consists of $n$ beads.
For $i \geq 0$ let $C_i$ be the unique elongation of $\sigma$ by $w[1..i]$, that is, foldable by $\Xi$. Hence $C_0 = \sigma$.

Let us consider the stabilization of the $i$-th bead $a_i$ upon $C_{i-1}$. The bead cannot collaborate with any succeeding bead $w[i+1],w[i+2],\cdots$ at delay 1. There are just two ways to get stabilized at delay 1. One way is to be bound to another bead. The other way is through a $tunnel\ section$. A tunnel section consists of four beads that occupy four neighbors of a point (Fig.\ref{TTT_tunnel_intro}). 
Accordingly, how they are stabilized can be described by a sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section. 
We let $S$ take the value $\blacksquare$ for halt.

@@

>>>>

Let $\Xi = (\Sigma, R, \delta, \alpha, \sigma, w)$ be a deterministic oritatami system of delay 1. 
For $i \geq 0$ let $C_i$ be the unique elongation of $\sigma$ by $w[1..i]$, that is, foldable by $\Xi$. Hence $C_0 = \sigma$.

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{ccc}

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}
          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.05];
            \node[above] at (180:1) {$p^\prime$};
            \node[above] at (0:1) {$p^\prime$};

            \foreach \theta in {0,180}{
              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
            }

            \foreach \theta in {60,-60,120,-120}{
              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }
          \end{scope}

          \node at (2,0) {Type S};
        \end{tikzpicture}
      \end{minipage}

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}

          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.05];
            \node[above] at (180:1) {$p^\prime$};
            \node[above] at (-60:1) {$p^\prime$};

            \foreach \theta in {-60,180}{
              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
            }

            \foreach \theta in {0,60,120,-120}{
 	            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }
          \end{scope}

          \node at (2,0) {Type O};
        \end{tikzpicture}
      \end{minipage}

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}

          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.05];
            \node[above] at (180:1) {$p^\prime$};
            \node[above] at (-120:1) {$p^\prime$};

            \foreach \theta in {-120,180}{
              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
            }

            \foreach \theta in {0,60,-60,120}{
              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
            }
          \end{scope}

          \node at (2,0) {Type A};
        \end{tikzpicture}
      \end{minipage}

    \end{tabular}
    \caption{Tunnel sections of all possible three types: straight (Type S), obtuse turn (Type O), and acute turn (Type A).}
    \label{fig:TTT_tunnel}
  \end{center}
\end{figure}

At delay 1, a bead cannot collaborate with its successors in order to stabilize itself. 
In fact, there are just two ways for a bead to get stabilized at delay 1 (or the bead has no place to be stabilized around so that the system halts). 
One is to be bound and the other is through a 1-in-1-out structure called the tunnel section. 
See Fig.~\ref{fig:TTT_tunnel}. 
A \textit{tunnel section} consists of four beads that occupy four neighbors of one point.

Let us consider the stabilization of the $i$-th bead $w[i]$ of the transcript $w$ upon $C_{i-1}$. 
The bead cannot collaborate with any succeeding bead $w[i+1],w[i+2],\cdots$ at delay 1. There are just two ways to get stabilized at delay 1. One way is to be bound to another bead. The other way is through a $tunnel\ section$. A tunnel section consists of four beads that occupy four neighbors of a point (Fig.\ref{TTT_tunnel_intro}). 
Accordingly, how they are stabilized can be described by a sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section. 
We let $S$ take the value $\blacksquare$ for halt.
